Post-Disturbance Diversity Trajectories in a Neotropical Forest

### 2018-02-06 Manuscript1.Rmd
test
set up affiliations

---
title: "Post-Disturbance Diversity Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Department of Ecology, University of Edimburgh
    address: >
      Street address,
      Zip code,
      Country.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal 00679993
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >  # Pour coordonne les packages LateX (supplémentaires)
  \usepackage{amsmath}
bibliography: references.bib # .bib à activer seulement pour git et word format (pandoc fait la biblio)
csl: 
lang: english # french
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook
#   bookdown::pdf_book:
#     base_format: EcoFoG::article
#     keep_tex: TRUE
#  bookdown::word_document2
#Mettre un code dans les figures pour indiquer le code d'où elle provient. ../ pour référer à des sous dossiers
---

@@

# Introduction
The large areas covered with tropical forests worldwide hold crucial commercial, social and cultural value. 
They provide wood and multiple non-timber forest products, shelter a diversified fauna, regulate local climate and support nutrients, water and carbon cycles and ensure cultural and human well-being. 
The demand for forests products and the shrink of unmanaged areas increased the human pressure on forests and currently threaten the maintenance of their structure, composition and function. 
The increasing demand for forests products, land-use changes and other human disturbances along with substantial climatic changes make a crucial issue of understanding the response of forests dynamics to such disturbance regimes [@Gibson2011a; @Morales-Hidalgo2015]. 
This has been addressed from the point of view of biomass production and carbon storage which resilience proved subjected to identified cyclic dynamics and therefore gives hope for the maintenance of forest ecosystem and their services. 
The response of trees biological diversity however has been sparsely studied, although this diversity is a major determinant of forests productivity, stability and functioning as it ensures interspecific complementarity, enhances the use of resources and the store of nutrients, and mitigates the prejudices of diseases and herbivory [@Tilman2014]. 
Maintain the integrity of forests functioning thus requires highlighting the impacts and underlying mechanisms of disturbance on trees diversity and question the extent of their resilience. 
Disturbance alter the biotic and abiotic parameters of the ecosystem in modifying the light availability, the heat and water fluxes, the plants productivity, etc. 
Although those changes proved impacting the proportion and identity of species, negligible or even positive impacts were highlighted when considering the community as a whole, in accordance with the intermediate disturbance hypothesis (IDH). 
The IDH that predicts a maximized species diversity at intermediate level of disturbance, however, mainly rely on the study of species richness which gives limited or even misleading information on forests recovery and functioning.
To have a detailed understanding of forests response to disturbance it is essential to identify the subsequent impact on species identity per se, which underlies any diversity change, as well as on richness, equitability and functional profile of the whole community.
Such combination of composition and diversity in browsing all facets of stands assemblage would highlight their resilience to perturbation, and its determinant and underlying ecological processes.
Disturbance survey would first assess species turnover and communities convergence through stands taxonomic composition and unveil environmental filters through functional composition that is based on the biological attributes of plants. 
The set of functional traits chosen for this functional analysis considers functional traits representative of species functional strategy, fitness, and ecology as it is the case for traits of the leaf or stem economics.
Composition analysis would be continued with diversity analysis assessing for the whole community the richness and evenness of the taxonomic and functional abundance distribution.   
Here we examined the long-term trajectory, in the sense of the evolution along time, of tropical forests taxonomic and functional composition and diversity. 
We studied the regular inventories over 30 years of twelve Amazonian forest plots, either untouched or disturbed with three disturbance intensity . 
The inventories were combined with one of the largest functional trait database for tropical trees. We aimed to (i) explicit the impact of disturbance on the long-term trajectory of tropical forest communities composition and diversity, (ii) question the long-term convergence of the composition of communities and (iii) determine their resilience or not, after disturbance.

>>>>

---
title: "Post-Disturbance Diversity Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal 00679993
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >  # Pour coordonne les packages LateX (supplémentaires)
  \usepackage{amsmath}
bibliography: references.bib # .bib à activer seulement pour git et word format (pandoc fait la biblio)
csl: 
lang: english # french
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook
#   bookdown::pdf_book:
#     base_format: EcoFoG::article
#     keep_tex: TRUE
#  bookdown::word_document2
#Mettre un code dans les figures pour indiquer le code d'où elle provient. ../ pour référer à des sous dossiers
---

@@

# Introduction
The large areas covered with tropical forests worldwide hold crucial economic, social and cultural value. 
They provide wood and multiple non-timber forest products, shelter a diversified fauna, regulate local climate and support nutrients, water and carbon cycles and ensure cultural and human well-being. 
The demand for forests products and the shrink of unmanaged areas increased the human pressure on forests and currently threaten the maintenance of their structure, composition and function. 
The increasing demand for forests products, land-use changes and other human disturbances along with substantial climatic changes make a crucial issue of understanding the response of forests dynamics to such disturbance regimes [@Gibson2011a; @Morales-Hidalgo2015]. 
This has been addressed from the point of view of biomass production and carbon storage which resilience proved subjected to identified cyclic dynamics and therefore gives hope for the maintenance of forest ecosystem and their services. 
The response of trees biological diversity however has been sparsely studied, although this diversity is a major determinant of forests productivity, stability and functioning as it ensures interspecific complementarity, enhances the use of resources and the store of nutrients, and mitigates the prejudices of diseases and herbivory [@Tilman2014]. 
Maintain the integrity of forests functioning thus requires highlighting the impacts and underlying mechanisms of disturbance on trees diversity and question the extent of their resilience. 
Disturbance alter the biotic and abiotic parameters of the ecosystem in modifying the light availability, the heat and water fluxes, the plants productivity, etc. 
Although those changes proved impacting the proportion and identity of species, negligible or even positive impacts were highlighted when considering the community as a whole, in accordance with the intermediate disturbance hypothesis (IDH). 
The IDH that predicts a maximized species diversity at intermediate level of disturbance, however, mainly rely on the study of species richness which gives limited or even misleading information on forests recovery and functioning.
To have a detailed understanding of forests response to disturbance it is essential to identify the subsequent impact on species identity per se, which underlies any diversity change, as well as on richness, equitability and functional profile of the whole community.
Such combination of composition and diversity in browsing all facets of stands assemblage would highlight their resilience to perturbation, and its determinant and underlying ecological processes.
Disturbance survey would first assess species turnover and communities convergence through stands taxonomic composition and unveil environmental filters through functional composition that is based on the biological attributes of plants. 
The set of functional traits chosen for this functional analysis considers functional traits representative of species functional strategy, fitness, and ecology as it is the case for traits of the leaf or stem economics.
Composition analysis would be continued with diversity analysis assessing for the whole community the richness and evenness of the taxonomic and functional abundance distribution.   
Here we examined the long-term trajectory, in the sense of the evolution along time, of tropical forests taxonomic and functional composition and diversity. 
We studied the regular inventories over 30 years of twelve Amazonian forest plots, either untouched or disturbed with three disturbance intensity . 
The inventories were combined with one of the largest functional trait database for tropical trees. We aimed to (i) explicit the impact of disturbance on the long-term trajectory of tropical forest communities composition and diversity, (ii) question the long-term convergence of the composition of communities and (iii) determine their resilience or not, after disturbance.
